Reproducible Plant Pathology

### 2017-04-23 README.rmd
Use svg not png; remove coverage

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/phytopathology/Reproducible.Plant.Pathology/commits/master) 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.png?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology) 
[![codecov.io](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology/coverage.svg?branch=master)](https://codecov.io/github/phytopathology/Reproducible.Plant.Pathology?branch=master)

>>>>

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/phytopathology/Reproducible.Plant.Pathology/commits/master) 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology.svg?branch=master)](https://travis-ci.org/phytopathology/Reproducible.Plant.Pathology)
